Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-09-20 article.tex

\hl{Define properties for three cases: i, ii and iii}
The Young's modulus $E = 206.9$ MPa and Poisson's ratio $\nu=0.29$, with the yield stress $\sigma_y$ given as \citep{Simo1992}
\begin{eqnarray}
	\sigma_y = \sigma_Y + H\bar{\varepsilon}_p + (\sigma_{\infty} - \sigma_Y)(1- e^{-\delta\bar{\varepsilon}_p})
\end{eqnarray}
The plastic yielding parameters are $\sigma_Y = 0.45$ MPa, $\sigma_{\infty} = 0.715$ MPa, $\delta = 16.93$, and $H = 0.12924$ MPa, where the hardening variable $\bar{\varepsilon}_p$ corresponds to equivalent plastic strain.

\hl{Give mesh details}

\hl{Add figures: finest mesh stress distributions and deformation}
\hl{Add figures: corner displacement prediction vs average cell width}

>>>>

The Young's modulus $E = 206.9$ MPa and Poisson's ratio $\nu=0.29$, with the yield stress $\sigma_y$ given as \citep{Simo1992}
\begin{eqnarray}
	\sigma_y = \sigma_Y + H\bar{\varepsilon}_p + (\sigma_{\infty} - \sigma_Y)(1- e^{-\delta\bar{\varepsilon}_p})
\end{eqnarray}
The plastic yielding parameters are $\sigma_Y = 0.45$ MPa, $\sigma_{\infty} = 0.715$ MPa, $\delta = 16.93$, and $H = 0.12924$ MPa, where the hardening variable $\bar{\varepsilon}_p$ corresponds to equivalent plastic strain.

\newpage
\hl{Define properties for three cases: i, ii and iii}

\renewcommand{\arraystretch}{2}
\begin{table}[h!]
%\resizebox{\textwidth}{!}{
\begin{tabular}{l|l}
i &  $t_y=6.25$ MPa, $E=70$ MPa, $\nu=1/3$ \\ \hline
ii & $t_y=0.0625$ MPa $E=1.0985$ MPa, $\nu=0.3$   \\ \hline
\multicolumn{1}{c|}{\multirow{2}{*}{iii}} & $t_y=0.3125$ MPa $E=206.9$ MPa, $\nu=0.29$, $\sigma_y = \sigma_Y + H\bar{\varepsilon}_p + (\sigma_{\infty} - \sigma_Y)(1- e^{-\delta\bar{\varepsilon}_p})$ \\[-0.5em]
\multicolumn{1}{c|}{} & $\sigma_Y = 0.45$ MPa, $\sigma_{\infty} = 0.715$ MPa, $\delta = 16.93$, $H = 0.12924$ MPa
\end{tabular}%
%}
\end{table}
\renewcommand{\arraystretch}{1}
\noindent
\textbf{Sources for case i:} \cite{Zienkiewicz2000}\\
O.C. Zienkiewicz, R.L. Taylor. The finite element method. Butterworth Heinemann, 2000.\\
https://www.simplassoftware.com/benchmarks.html\#biblio-58\\
https://github.com/spolanski/CoFEA/tree/master/benchmarks/02-cooks-membrane\\
\textbf{Sources for case ii:} \cite{dealII95}\\
https://www.dealii.org/current/doxygen/deal.II/code\_gallery\_Quasi\_static\_Finite\_strain\_Compressible\_Elasticity.html\\
\textbf{Sources for case iii:} \citep{Simo1992}

\hl{Give mesh details}\\
mesh.1 - 3x3 - 9 CVs\\
mesh.2 - 6x6 - 36 CVs\\
mesh.3 - 12x12 - 144 CVs\\
mesh.4 - 24x24 - 576 CVs\\
mesh.5 - 48-48 - 2304 CVs\\
mesh.6 - 96x96 - 9216 CVs\\
mesh.7 - 192x192 - 36864 CVs

\hl{dd figures: finest mesh stress distributions and deformation Add figures: corner displacement prediction vs average cell width}

\begin{figure}[h!]
   \centering
	\subfigure[Equivalent stress distribution for the mesh with $368\,642$ cells (case ii)]
	{
		\includegraphics[height=0.42\textwidth]{figures/cooksMembrane-sigmaEq.pdf}  
	}
	\subfigure[Convergence of tip (48,60) vertical displacement, normalized using the displacement value from the finest mesh (given in parentheses)]
	{
		\includegraphics[height=0.32\textwidth]{figures/cooksMembrane-tipDispConvergence.pdf} 
	}
   \caption{Convergence of tip displacement and equivalent stress for hyperelastic case.}
   \label{fig:narrowTmember_sigmaEq}
\end{figure}
@Philip, scale for cooksMembrane-sigmaEq.pdf should be from 0 to 0.2 MPa.
